 Allocation scoring rules as a generalization of quantile scoring rules

### 2023-04-17 notes/allocation_notes.rmd
rewriting/correcting expected score derivations

---
title: " Allocation scoring rules as a generalization of quantile scoring rules"
date: "`r Sys.Date()`"
output: 
    pdf_document:
        latex_engine: xelatex
urlcolor: blue
bibliography: allocation.bib 
header-includes:
   - \usepackage{amsmath}
   - \usepackage{algorithm}
   - \usepackage[noend]{algpseudocode}
   - \usepackage{amsthm}
   - \usepackage{bm}
   - \usepackage{cases}
   - \usepackage{caption}
   - \usepackage{unicode-math}
   - \usepackage{hyperref}
   - \DeclareMathOperator*{\argmin}{argmin}

---

@@

By making the forecaster aware of $s$ prior to prediction, we elicit an $\alpha$-level quantile $q_{\alpha,F}$ of the forecast distribution $F$ for $Y$. That is, if a forecaster believes that $Y \sim F$, then according to this belief they minimize their expected score
\begin{align} 
\sbar_F(x) = E_F[s(x,Y)]  &= O E_F[(g(x) - g(Y))\sb{+}] + U E_F[(g(x) - g(Y))\sb{-}] \label{eqn:scalar_obj}\\
&= O\int_{-\infty}^x(g(x) - g(y))f(y)dy + U\int_x^{\infty}(g(y) - g(x))f(y)dy \label{eqn:scalar_obj_int}
\end{align}
by forecasting a quantile $q_{\alpha, F} \in Q_F\left(\alpha\right)$ which solves the first order equation
\begin{align}
\nonumber 0 =\frac{d}{dx}\sbar_F(x) 
&= O E_F\left[\frac{d}{dx}(g(x) - g(Y))\sb{+}\right] + U E_F\left[\frac{d}{dx}(g(x) - g(Y))\sb{-}\right] \\
&= O E_F[g^{\prime}(x)\mathbb{1}\{Y < x\}] + U E_F[-g^{\prime}(x)\mathbb{1}\{Y \geq x\}] \\
&= O g^{\prime}(x) \mathbb{P}_F(Y<x) - U g^{\prime}(x) \mathbb{P}_F(Y\geq x) \\
&= g^{\prime}(x)\left( O F(x) - U (1-F(x))\right) \\
&= \kappa g^{\prime}(x)\left(F(x) - \alpha\right) \label{scalar_Z_deriv}.
\end{align}
(See \hyperref[scalar_Z_deriv_detail]{appendix} for an alternative derivation in terms of a density.)
The critical point $q_{\alpha, F}$ is actually a minimum since \eqref{scalar_Z_deriv} is non-positive on $\{x<q_{\alpha, F}\}$ and non-negative on $\{x>q_{\alpha, F}\}$.
 When $g^{\prime}(q)>0$, this minimum is unique since
\begin{align}
   \frac{d^2}{dx^2}\sbar_F(x)\big|_{x=q_{\alpha, F}} &= 
   \kappa\left(g^{\prime}(x)f(x) + g^{\prime \prime}(x)\left(F(x) - \alpha\right)\right)\big|_{x=q_{\alpha, F}} \label{scalar_Z_deriv2}\\
   &=\kappa(g^{\prime}(q_{\alpha, F})f(q_{\alpha, F}) + g^{\prime \prime}(q_{\alpha, F})\cdot 0) >0.
\end{align}

@@

Note that $\frac{d}{dx}\sbar_F(x) =\frac{d}{dx}E_F[s(x,Y)] = h(x)E_F[V(x,Y)]$, where $h(x) = \kappa g^{\prime}(x)$ and 
\begin{align}
V(x,y) &\coloneq (1-\alpha)\mathbb{1}\{y<x\} - \alpha \mathbb{1}\{y \geq x\} \mathrel{\phantom{=}}\\
&= (1-\alpha)\mathbb{1}\{y<x\} - \alpha \left(1 - \mathbb{1}\{y<x\}\right) \\
&= \mathbb{1}\{y<x\} - \alpha. 
\end{align}
By virtue of $E_F[V(Q_F(\alpha),Y)]=0$, $V$ is said to be an \emph{identification function} for the $\alpha$ quantile. The fact that, generally speaking, any elicitable functional (such as a quantile) has an identification function is known as \emph{Osband's principle}.

@@

Using $u_- = u_+ - u$, the objective function \eqref{eqn:scalar_obj} can also be helpfully rewritten as
\begin{align}
\nonumber \sbar_F(x) &= OE_F[(g(x) - g(Y))\sb{+}] + U E_F[(g(x) - g(Y))\sb{+}] - U E_F[(g(x) - g(Y))] \\ 
\nonumber  &= (O+U)E_F[(g(x) - g(Y))\sb{+}] - U E_F[(g(x) - g(Y))] \\
&= (O+U) \int_{-\infty}^{x} (g(x) - g(y))f(y)dy - Ug(x)+ U \overline{g}\sb{F} \label{obj_integral}\\
&= (O+U)\left(g(x)F(x) - \overline{g}_F(x) \right) - Ug(x) + U\overline{g}\sb{F}) \label{obj_sep}\\
&= \kappa\left[g(x)(F(x) - \alpha) -\overline{g}_F(x) + \alpha \overline{g}\sb{F}\right] \label{obj_pexp} 
\end{align}
where $\overline{g}_F(x) = E_F[g(Y)\mathbb{1}\{Y \leq x\}]$, and $\overline{g}\sb{F} = E_F[g(Y)]$.

@@

@@

## Examples for various forecaster beliefs

### 1) $Y \sim U[a,b]$

Here $F(x) = \mathbb{1}\{a<x<b\}(x-a)/(b-a) + \mathbb{1}\{b \leq x\}$ in \eqref{obj_pexp} gives 
<!--  
&= 
\begin{cases}
\frac{U}{b-a}\int_a^b (g(y) - g(x))dy & x\leq a \\[8pt]
\frac{O}{b-a}\int_a^x (g(x) - g(y))dy + \frac{U}{b-a}\int_x^b (g(y) - g(x))dy & a < x < b \\[8pt]
\frac{O}{b-a}\int_a^b (g(x) - g(y))dy & b \leq x 
\end{cases} \\ 
-->
\begin{align}
\sbar_F(x) &= 
\begin{cases}
\frac{\kappa}{b-a}\left( - \alpha(b-a)g(x) + \alpha\int_a^b g(y)dy\right) & x\leq a \\[8pt]
\frac{\kappa}{b-a}\left((x-a- \alpha(b-a))g(x) - \int_a^x g(y)dy + \alpha\int_a^b g(y)dy\right) & a < x < b \\[8pt]
\frac{\kappa}{b-a}\left((1-\alpha)(b-a)g(x) -(1-\alpha)\int_a^b g(y)dy \right) & b \leq x
\end{cases} 
\end{align}

When $g(x)=x$ this becomes
\begin{align}
\sbar_F(x) &= 
\begin{cases}
\frac{\kappa}{b-a}\left( - \alpha(b-a)x + \frac{\alpha}{2}(b^2-a^2)\right) & x\leq a \\[8pt]
\frac{\kappa}{b-a}\left((x-a- \alpha(b-a))x - \frac{1}{2}(x^2 - a^2) + \frac{\alpha}{2}(b^2-a^2)\right) & a < x < b \\[8pt]
\frac{\kappa}{b-a}\left((1-\alpha)(b-a)x -\frac{(1-\alpha)}{2}(b^2-a^2)\right) & b \leq x
\end{cases} \\
&= 
\begin{cases}
-\kappa\alpha\left[x - \frac{a+b}{2}\right] & x\leq a \\[8pt]
\frac{\kappa}{2}\left[\frac{1}{b-a}(x - (a+\alpha(b-a)))^2 +\alpha(1-\alpha)(b-a)\right] & a < x < b \\[8pt]
\kappa(1-\alpha)\left[ x - \frac{a+b}{2}\right] & b \leq x
\end{cases}
\end{align}

Thus $\sbar_F(x)$ has the form of pinball loss centered on the mean $\mu_Y = \frac{a+b}{2}$ and interpolated on $(a,b)$ 
 by a quadratic centered at the quantile $a+\alpha(b-a)$ with slopes matching the linear tails at $a$ and $b$.

alphas = c(.1,.4,.5,.9)
p_unif <- plot_loss(
  alphas = alphas,
  lossfun = unif_loss, 
  parms = list(min = 0, max = 1), 
  pfun = punif, 
  qfun = qunif,
  mag = 1, 
  xl = -1.5, 
  xr = 2.5,
  yb = 0
  ) + ggtitle("Unif(0,1)")
```

### 2) $g(x)=x$ and $F_Y=F_{\mu, \sigma}$ lies in a location-scale family

That is, $Y = \mu + \sigma Z$ and $Z \sim F_Z = F_0$. Then $f_Y(y) = \dby{}{z} F_Z\left(\frac{y-\mu}{\sigma}\right)\dby{z}{y} = f_Z(z)/\sigma$ and so
\begin{align}
\overline{g}_F(x) = \int_a^x y f_Y(y)dy &= \int_{\frac{a-\mu}{\sigma}}^{\frac{x-\mu}{\sigma}}(\mu + \sigma z)f_Z(z)dz \\
& = \mu F_Z\left(\frac{x-\mu}{\sigma}\right) + \sigma \int_{\frac{a-\mu}{\sigma}}^{\frac{x-\mu}{\sigma}}zf_Z(z)dz\\
& =\mu F_Y(x) + \sigma \mu_{F_0}\left(\frac{x-\mu}{\sigma}\right).
\end{align}
where $\mu_{F_0}(u) = \int_{\frac{a-\mu}{\sigma}}^{u} zf_0(z)dz$. This gives
<!-- With the change of variables $y=Q_F(\alpha) = F^{-1}(\alpha), dy =  d(F^{-1}(\alpha)) = \frac{d\alpha}{f(y)}$, we have
\begin{align}
\overline{g}_F(x) = \int_a^x y f_Y(y)dy = \int_{0}^{F(x)}Q_F(\alpha)d\alpha 
& = \mu F(x) + \sigma \int_0^{F(x)} Q_0(\alpha)d\alpha \\
& =\mu F(x) + \sigma \mu_{F_0}\left(\frac{x-\mu}{\sigma}\right).
\end{align} -->
\begin{align}
\nonumber \sbar_F(x) &= \kappa\left[x(F(x) - \alpha) - \mu F(x) - 
\nonumber \sigma \mu_{F_0}\left(\frac{x-\mu}{\sigma}\right) + \alpha \mu \right]  \\
&= \kappa\left[\left(F(x) - \alpha\right)(x-\mu)- \sigma \mu_{F_0}\left(\frac{x-\mu}{\sigma}\right) \right]
\label{lc-form}
\end{align}

### 3) $g(x)=x$ and $Y \sim N(\mu,\sigma)$

When $F=\Phi_{\mu,\sigma}$, $\mu_{F_0}\left(\frac{x-\mu}{\sigma}\right)=-\sigma \varphi_{\mu, \sigma}(x)$, giving $q(\alpha)$ as the minimum of 
$$
Z_F(x) = \kappa\left[(\Phi_{\mu,\sigma}(x) - \alpha)(x-\mu) + \sigma^2 \varphi_{\mu, \sigma}(x)\right].
$$

```{r echo = FALSE, cache=TRUE}
norm_loss <- function(alpha, mean, sd) {
  f <- function(x){
    alpha^(-1)*((pnorm(x, mean, sd)-alpha)*(x-mean) + sd^2*dnorm(x,mean,sd))
  }
  return(f)
}
parms = list(mean = 0, sd = 2)
p_norm <- plot_loss(
    alphas = alphas,
    lossfun = norm_loss, 
    parms = parms, 
    pfun = pnorm, 
    qfun = qnorm,
    mag = 10, 
    xl = -6, 
    xr = 6,
    yb = 0
) + ggtitle("Normal(0,2)")
```

### 4) $g(x)=x$ and $Y \sim \mathrm{Exp}(1/\sigma)$

Taking $\mu \equiv 0, Y = \sigma Z$ and $F_Z(x) = F_0(x) = \mathbb{1}\{0 \leq x\}(1 - e^{-x})$ we have
 $\mu_{F_0}(x) = \mathbb{1}\{0 \leq x\}(1 - e^{-x}(1+x))$. Then \eqref{lc-form} is

\begin{align}
\nonumber \sbar_F(x) &= 
\mathbb{1}\{0 \leq x\}\kappa\left[F(x)x - \sigma \mu_{F_0}\left(\frac{x}{\sigma}\right) \right] - \kappa\alpha x\\
&= \mathbb{1}\{0 \leq x\}\kappa
\left[
\left(1 - e^{-x/\sigma}\right)x - \sigma \left(1- e^{-x/\sigma}\left(1+\frac{x}{\sigma}\right) \right)
\right] - \kappa\alpha x\\
&= \mathbb{1}\{0 \leq x\}\kappa\left[ \sigma e^{-x/\sigma} + x - \sigma \right] - \kappa\alpha x
\end{align}

```{r echo = FALSE, cache=TRUE}
exp_loss <- function(alpha, rate) {
  f <- function(x){
    ((exp(-x*rate)*rate^(-1) + x - rate^(-1)))*(x>0) - alpha*x
  }
  return(f)
}
parms = list(rate = 1)
p_exp <- plot_loss(
    alphas = alphas,
    lossfun = exp_loss, 
    parms = parms, 
    pfun = pexp, 
    qfun = qexp,
    mag = 3, 
    xl = -2, 
    xr = 5,
    yb = -1
) + ggtitle("Exp(1)")
```

## Another form for $\sbar_F(x)$

There also may be situations where it is convenient to integrate the $(O+U)$-term in \eqref{obj_sep} by parts to get 
\begin{align}
\sbar_F(x) = \kappa\left[\int_a^x g^{\prime}(y)F(y)dy - \alpha(g(x) - \overline{g}\sb{F})\right]. \label{obj_intF}
\end{align}

@@

In the inventory management literature, minimization of an expectation of the form of $\sbar_F(x)$ for a given $F$ arises in the \emph{newsvendor problem}.  This involves the ordering decision faced by a retailer of a perishable good (such as newpapers) when customer demand is uncertain. Because the focus here is on revenues and expenditures, terms other than just the over- and underprediction penalties in \eqref{eqn:scalar_score} often appear, giving a retailer's scoring function as
\begin{align}
s_n(x,y) & = a_x x +a_y y +a_{+}(x-y)_+ + a_{-}(x-y)_-.
\end{align}
We might have, for example, the score given by net value transfers
\begin{align}
s_n(x,y) = cx-py - u(x-y)_+ + (p+r)(x-y)_-
\end{align}
where $x$ newspapers are ordered at price $c$, $y - (x-y)_-$ are sold at retail price $p$, $(x-y)_+$ are sold at salvage price $u$, 
and $r(x-y)_-$ of customer "goodwill" is lost. 
This can be rewritten as
\begin{align}
s_n(x,y) &= (a_{+} + a_x)(x-y)_+ + (a_{-} - a_x)(x-y)_- +(a_x + a_y)y \\
&= (c-u)(x-y)_+ + (p+r-c)(x-y)_- -(p-c)y
\end{align}
giving the retailer's objective function under a demand distribution $F$ as
\begin{align}
\sbar_{n,F}(x) = (a_{+} + a_x)E_F[(x-Y)_+] + (a_{-} - a_x)E_F[(x-Y)_-] +(a_x + a_y)E[Y].
\end{align}
This differs by a constant from our $\sbar_F(x)$ in \eqref{eqn:scalar_obj} after taking $g(x)=x$, $O=a_{+} + a_x=c-u$ 
and $U=a_{-} - a_=p+r-c$, and so has the same minimizer   
\begin{align}
Q = F^{-1}\left(\frac{U}{O+U}\right) =  F^{-1}\left(\frac{a_{-} - a_x}{a_{-} + a_{+}}\right) 
= F^{-1}\left(\frac{p+r-c}{p+r-u}\right).
\end{align}
Note, for reference, that in the literature $\sbar_{n,F}(x)$ is often encountered in the form of \eqref{obj_integral}:
\begin{align}
&(O+U) \int_{0}^{x} (x - y)f(y)dy - Ux+ (U+a_x+a_y)E[Y] \\
=\,&(p+r-u) \int_{0}^{x} (x - y)f(y)dy - (p+r-c)x+ rE[Y]
\end{align}

@@

@@

According to \eqref{eqn:scalar_obj_int} and \eqref{obj_pexp} the objective function is now
\begin{align}
\sbar_F(\mathbf{x})&= \sum_{i=1}^{N} \sbar_{F_i}(x_i) = \sum_{i=1}^{N} \left\{O_i\int_{-\infty}^{x_i}(g_i(x_i) - g_i(y))f_i(y)dy + 
U_i\int_{x_i}^{\infty}(g_i(y) - g_i(x_i))f_i(y)dy \right\} \\
&= \sum_{i=1}^{N} \kappa_i
\left[
g_i(x_i)(F_i(x_i) - \alpha_i) -\overline{g_i}_{F_i}(x_i) + \alpha_i \overline{g_i}\sb{F_i}
\right] 
\end{align}

>>>>

---
title: " Allocation scoring rules as a generalization of quantile scoring rules"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    latex_engine: xelatex
urlcolor: blue
bibliography: allocation_notes.bib 
header-includes:
   - \usepackage{amsmath}
   - \usepackage{algorithm}
   - \usepackage[noend]{algpseudocode}
   - \usepackage{amsthm}
   - \usepackage{bm}
   - \usepackage{cases}
   - \usepackage{caption}
   - \usepackage{unicode-math}
   - \usepackage{hyperref}
   - \DeclareMathOperator*{\argmin}{argmin}
---

@@

By making the forecaster aware of $s$ prior to prediction, we elicit an $\alpha$-level quantile $q_{\alpha,F}$ of the forecast distribution $F$ for $Y$. To see this, notice that if a forecaster believes that $Y \sim F$, they will calculate their expected score to be
\begin{align} 
\sbar_F(x) = E_F[s(x,Y)]  &= O E_F[(g(x) - g(Y))\sb{+}] + U E_F[(g(x) - g(Y))\sb{-}]. \label{eqn:scalar_obj}
\end{align}
In order to minimize this expectation, they must forecast a solution of the first order equation
\begin{align}
\nonumber 0 =\frac{d}{dx}\sbar_F(x) 
&= O E_F\left[\frac{d}{dx}(g(x) - g(Y))\sb{+}\right] + U E_F\left[\frac{d}{dx}(g(x) - g(Y))\sb{-}\right] \\
&= O E_F[g^{\prime}(x)\mathbb{1}\{Y < x\}] + U E_F[-g^{\prime}(x)\mathbb{1}\{Y \geq x\}] \\
&= O g^{\prime}(x) \mathbb{P}_F(Y<x) - U g^{\prime}(x) \mathbb{P}_F(Y\geq x) \\
&= g^{\prime}(x)\left( O F(x) - U (1-F(x))\right) \\
&= \kappa g^{\prime}(x)\left(F(x) - \alpha\right), \label{scalar_Z_deriv}
\end{align}
that is, a quantile $q_{\alpha, F} \in Q_F\left(\alpha\right)$.
(See \hyperref[scalar_Z_deriv_detail]{appendix} for an alternative derivation in terms of a density.)
The critical point $q_{\alpha, F}$ is actually a minimum since \eqref{scalar_Z_deriv} is non-positive on $\{x<q_{\alpha, F}\}$ and non-negative on $\{x>q_{\alpha, F}\}$.
 When $g^{\prime}(q)>0$, this minimum is unique since
\begin{align}
   \frac{d^2}{dx^2}\sbar_F(x)\big|_{x=q_{\alpha, F}} &= 
   \kappa\left(g^{\prime}(x)f(x) + g^{\prime \prime}(x)\left(F(x) - \alpha\right)\right)\big|_{x=q_{\alpha, F}} \label{scalar_Z_deriv2}\\
   &=\kappa(g^{\prime}(q_{\alpha, F})f(q_{\alpha, F}) + g^{\prime \prime}(q_{\alpha, F})\cdot 0) >0.
\end{align}

@@

Note that $\frac{d}{dx}\sbar_F(x) =\frac{d}{dx}E_F[s(x,Y)] = h(x)E_F[V(x,Y)]$, where $h(x) = \kappa g^{\prime}(x)$ and 
\begin{align}
V(x,y) &\coloneq (1-\alpha)\mathbb{1}\{y < x\} - \alpha \mathbb{1}\{y \geq x\} \mathrel{\phantom{=}}\\
&= (1-\alpha)\mathbb{1}\{y < x\} - \alpha \left(1 - \mathbb{1}\{y < x\}\right) \\
&= \mathbb{1}\{y < x\} - \alpha. 
\end{align}
By virtue of $E_F[V(Q_F(\alpha),Y)]=0$, $V$ is said to be an \emph{identification function} for the $\alpha$ quantile. The fact that, generally speaking, any elicitable functional (such as a quantile) has an identification function is known as \emph{Osband's principle}.

@@

## Examples of forecaster expected scores

Corresponding to the two expressions of an expectation $E_F[h(y)\mathbb{1}\{a < y<b\}]$ as either side of the Riemann-Stieltjes integration-by-parts 
formula $\int_{a}^{b}h(y)dF(y) = h(y)F(y) \big|_{a}^{b} - \int_{a}^{b}F(y)dh(y)$, the expected score \eqref{eqn:scalar_obj}
can be written as either
\begin{align}
\sbar_F(x) &= O \int_{\mathbb{R}} \int_{\mathbb{R}} \mathbb{1}\{Y \leq u < x\}dg(u) dF(y) + U \int_{\mathbb{R}} \int_{\mathbb{R}} \mathbb{1}\{x \leq u < Y\}dg(u) dF(y) \\
&= O \int_{\mathbb{R}} \mathbb{1}\{u < x\} F(u) dg(u) + U \int_{\mathbb{R}} \mathbb{1}\{u \geq x\} (1-F(u)) dg(u) \\
&= O \int_{-\infty}^x F(u) dg(u) + U \int_{x}^{\infty}(1-F(u)) dg(u), \label{eqn:scalar_obj_cdf_form} 
\end{align}
or
\begin{align}
\nonumber \sbar_F(x) &= O\int_{-\infty}^x(g(x) - g(y))dF(y) + U\int_x^{\infty}(g(y) - g(x))dF(y)\\ 
&= O\left(g(x)F(x) - \int_{-\infty}^x g(y)dF(y) \right) + U \left( \int_x^{\infty} g(y)dF(y) - g(x)(1-F(x))\right) \\
&= g(x)\left((O+U)F(x) - U\right) -  (O+U)\int_{-\infty}^x g(y)dF(y) + U \int_{\mathbb{R}} g(y)dF(y) \\
&= \kappa\left[g(x)(F(x) - \alpha) -\overline{g}_{F}(x) + \alpha \overline{g}\sb{F}\right] \label{eqn:obj_pexp} 
\end{align}
where 
\begin{align}
\overline{g}_F(x) &= E_{F}[g(Y)\mathbb{1}\{Y \leq x\}] \label{eqn:gbarx} \\
\overline{g}\sb{F} &= E_{F}[g(Y)]. \label{eqn:gbar}
\end{align}

@@

Taking, for example, $g(x)=x$ and $F = \mathrm{Exp}(1/\sigma)$, we have
\begin{align}
\overline{g}_{F}(x) = \int_{0}^{\max(0,x)} y \frac{e^{-y/\sigma}}{\sigma}dy = \mathbb{1}\{x \geq 0\} \left[\sigma-e^{-x / \sigma}(\sigma+x)\right]
\end{align}
so that
\begin{align}
\sbar_{\mathrm{Exp}(1/\sigma)}(x) 
&= \kappa\left[x(\mathbb{1}\{x \geq 0\} \left[1 -e^{-x / \sigma}\right]  - \alpha) - \mathbb{1}\{x \geq 0\} \left[\sigma-e^{-x / \sigma}(\sigma+x)\right] + \alpha\sigma\right] \\
&= \kappa\left[\mathbb{1}\{x \geq 0\}\sigma e^{-x / \sigma} + (\mathbb{1}\{x \geq 0\} - \alpha)(x-\sigma)\right].
\end{align}

If, on the other hand, $F=F_{\mu, \sigma}$ lies in a location-scale family, that is, $F(x)= F_0\left(\frac{x-\mu}{\sigma}\right)$, we have
\begin{align}
\int_{-\infty}^{x} y dF(y) &= \int_{-\infty}^{\frac{x-\mu}{\sigma}}(\mu + \sigma z)dF_0(z) \\
& = \mu F(x) + \sigma \int_{-\infty}^{\frac{x-\mu}{\sigma}}zdF_0(z).
\end{align}
Then \eqref{eqn:obj_pexp} becomes
\begin{align}
\sbar_F(x) &= \kappa\left[x(F(x) - \alpha) - \mu F(x) - \sigma \int_{-\infty}^{\frac{x-\mu}{\sigma}}zdF_0(z)  + \alpha E_F[Y]\right] \\
&= \kappa\left[F(x)(x-\mu) - \alpha(x - E_F[Y]) - \sigma \int_{-\infty}^{\frac{x-\mu}{\sigma}}zdF_0(z)\right] \label{eqn:lc-form}
\end{align}

For example, if $F = U[a,b]$ is uniform we can take $F_0 = U[0,1], \mu = a, \sigma = b-a$, and \eqref{eqn:lc-form} is
\begin{align}
\sbar_F(x) &= 
\begin{cases}
-\alpha\kappa\left[x - \frac{a+b}{2}\right] & x\leq a \\[8pt]
\kappa\left[\frac{x-a}{b-a}(x-a) -\alpha\left(x - \frac{a+b}{2}\right) -  (b-a) \frac{1}{2}\left(\frac{x-a}{b-a}\right)^2\right] & a < x < b \\[8pt]
\kappa\left[x - a -\alpha\left(x - \frac{a+b}{2}\right) - \frac{b-a}{2}\right] & b \leq x
\end{cases} \\
&=
\begin{cases}
-\kappa\alpha\left[x - \frac{a+b}{2}\right] & x\leq a \\[8pt]
\frac{\kappa}{2}\left[\frac{1}{b-a}(x - (a+\alpha(b-a)))^2 +\alpha(1-\alpha)(b-a)\right] & a < x < b \\[8pt]
\kappa(1-\alpha)\left[ x - \frac{a+b}{2}\right] & b \leq x
\end{cases}
\end{align}

Thus, outside $(a,b)$, $\sbar_{U[a.b]}(x)$ has the form of pinball loss centered on the mean $m_F = \frac{a+b}{2}$ and is interpolated on $(a,b)$ 
 by a quadratic centered at the quantile $a+\alpha(b-a)$ with slopes matching the linear tails at $a$ and $b$ (see figure 1).

Or if $F=\Phi_{\mu,\sigma}$ is normal with location $\mu = E_F[Y]$ and scale $\sigma = \sqrt{\mathrm{Var}(Y)}$, 
we have 
\begin{align}
\int_{-\infty}^{\frac{x-\mu}{\sigma}}zdF_0(z)=-\frac{1}{\sqrt{2\pi}}\exp\left\{-\frac{(x-\mu)^2}{2 \sigma^2}\right\} = - \sigma\varphi_{\mu, \sigma}(x)
\end{align}
so that
\begin{align}
\sbar_F(x) = \kappa\left[(\Phi_{\mu,\sigma}(x) - \alpha)(x-\mu) + \sigma^2 \varphi_{\mu, \sigma}(x)\right].
\end{align}

alphas = c(.1,.4,.5,.9)
p_unif <- plot_loss(
  alphas = alphas,
  lossfun = unif_loss, 
  parms = list(min = 0, max = 1), 
  pfun = punif, 
  qfun = qunif,
  mag = 1, 
  xl = -1.5, 
  xr = 2.5,
  yb = 0
  ) + ggtitle("Unif(0,1)")

norm_loss <- function(alpha, mean, sd) {
  f <- function(x){
    alpha^(-1)*((pnorm(x, mean, sd)-alpha)*(x-mean) + sd^2*dnorm(x,mean,sd))
  }
  return(f)
}
parms = list(mean = 0, sd = 2)
p_norm <- plot_loss(
    alphas = alphas,
    lossfun = norm_loss, 
    parms = parms, 
    pfun = pnorm, 
    qfun = qnorm,
    mag = 10, 
    xl = -6, 
    xr = 6,
    yb = 0
) + ggtitle("Normal(0,2)")

exp_loss <- function(alpha, rate) {
  f <- function(x){
    exp(-x*rate)*(rate^(-1))*(x>=0) + ((x>=0) - alpha)*(x - rate^(-1))
  }
  return(f)
}
parms = list(rate = 1)
p_exp <- plot_loss(
    alphas = alphas,
    lossfun = exp_loss, 
    parms = parms, 
    pfun = pexp, 
    qfun = qexp,
    mag = 3, 
    xl = -2, 
    xr = 5,
    yb = -1
) + ggtitle("Exp(1)")
```

We finally note that for non-trivial $g$'s it may be helpful to make the substitution $v=g(u)$ in \eqref{eqn:scalar_obj_cdf_form} to get
\begin{align}
\sbar_F(x) &=  O \int_{-\infty}^{g(x)} F(g^{-1}(u)) du + U \int_{g(x)}^{\infty}(1-F(g^{-1}(u))) du
\end{align}
and in \eqref{eqn:gbarx} to get
\begin{align}
\overline{g}_F(x) &= \int_{-\infty}^{g(x)}v d(F \circ g^{-1})(v).
\end{align}

@@

@@

In the inventory management literature, minimization of an expectation of the form of $\sbar_F(x)$ for a given $F$ arises in the \emph{newsvendor problem}.  This involves the ordering decision faced by a retailer of a perishable good (such as newpapers) when customer demand is uncertain. Because the focus here is on revenues and expenditures, terms other than just the over- and underprediction penalties in \eqref{eqn:scalar_score} often appear, giving a retailer's scoring function as
\begin{align}
s_n(x,y) & = a_x x +a_y y +a_{+}(x-y)_+ + a_{-}(x-y)_-.
\end{align}
We might have, for example, the score given by net value transfers
\begin{align}
s_n(x,y) = cx-py - u(x-y)_+ + (p+r)(x-y)_-
\end{align}
where $x$ newspapers are ordered at price $c$, $y - (x-y)_-$ are sold at retail price $p$, $(x-y)_+$ are sold at salvage price $u$, 
and $r(x-y)_-$ of customer "goodwill" is lost. 
This can be rewritten as
\begin{align}
s_n(x,y) &= (a_{+} + a_x)(x-y)_+ + (a_{-} - a_x)(x-y)_- +(a_x + a_y)y \\
&= (c-u)(x-y)_+ + (p+r-c)(x-y)_- -(p-c)y
\end{align}
giving the retailer's objective function under a demand distribution $F$ as
\begin{align}
\sbar_{n,F}(x) = (a_{+} + a_x)E_F[(x-Y)_+] + (a_{-} - a_x)E_F[(x-Y)_-] +(a_x + a_y)E[Y].
\end{align}
This differs by a constant from our $\sbar_F(x)$ in \eqref{eqn:scalar_obj} after taking $g(x)=x$, $O=a_{+} + a_x=c-u$ 
and $U=a_{-} - a_=p+r-c$, and so has the same minimizer   
\begin{align}
Q = F^{-1}\left(\frac{U}{O+U}\right) =  F^{-1}\left(\frac{a_{-} - a_x}{a_{-} + a_{+}}\right) 
= F^{-1}\left(\frac{p+r-c}{p+r-u}\right).
\end{align}
Note, for reference, that in the literature $\sbar_{n,F}(x)$ is often encountered in the form
\begin{align}
&(O+U) \int_{0}^{x} (x - y)f(y)dy - Ux+ (U+a_x+a_y)E[Y] \\{}
=\,&(p+r-u) \int_{0}^{x} (x - y)f(y)dy - (p+r-c)x+ rE[Y]
\end{align}

@@

There is considerable opportunity here for confusion as to the role of $x$ if one is following (as we mostly are) the notation of [@ehm2016quantiles].

@@

According to \eqref{eqn:scalar_obj} and \eqref{eqn:obj_pexp} the objective function is now
\begin{align}
\sbar_F(\mathbf{x})&= \sum_{i=1}^{N} \sbar_{F_i}(x_i) = \sum_{i=1}^{N} \left\{O_i\int_{-\infty}^{x_i}(g_i(x_i) - g_i(y))f_i(y)dy + 
U_i\int_{x_i}^{\infty}(g_i(y) - g_i(x_i))f_i(y)dy \right\} \\
&= \sum_{i=1}^{N} \kappa_i
\left[
g_i(x_i)(F_i(x_i) - \alpha_i) -\overline{g_i}_{F_i}(x_i) + \alpha_i \overline{g_i}\sb{F_i}
\right] 
\end{align}
